---
title: "Homework 0: Welcome to Advanced Data Science!"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

```


# Homework 0 Assignment

Here's a fun and perhaps surprising statistical riddle, and a good way to get some practice writing R functions.

## The Monty Hall Problem

In a gameshow, contestants try to guess which of 3 closed doors contain a cash prize (goats are behind the other two doors). Of course, the odds of choosing the correct door are 1 in 3. As a twist, the host of the show opens a door after a contestant makes his or her choice. This door is always one of the two the contestant did not pick, and is also always one of the goat doors (note that it is always possible to do this, since there are two goat doors). At this point, the contestant has the option of keeping his or her original choice, or swtiching to the other unopened door. The question is: is there any benefit to switching doors? The answer surprises many people who haven't heard the question before.

We can answer the problem by running simulations in R. We'll do it in several parts.

#### Problem 1

First, write a function called `simulate_prizedoor(nsims)` with the argument `nsims` representing the number of simulations to run. The output should return a set of integers (1s, 2, 3s) representing hiding a prize behind door 1, door 2 and door 3. The length of the returned object should be `nsims`. This function will simulate the location of the prize in many games.

```{r}
## add your code here

simulate_prizedoor <- function(x){
 door <-  length(x)
 return(door)}

```

#### Problem 2

Next, write a function that simulates the contestant's guesses for `nsims` simulations. Call this function `simulate_guess()`. This function should return any strategy for guessing which door a prize is behind. This could be a random strategy, one that always guesses 2, whatever. Include the `nsims` as an argument of the function. The output should return a set of integers (1s, 2, 3s) representing the guess for the contest, whether the prize is behind door 1, door 2 or door 3. The length of the returned object should be `nsims`. 

```{r}
## add your code here 

```

#### Problem 3 

Next, write a function, `goat_door()`, to simulate the opening of a "goat door" that doesn't contain the prize, and is different from the contestants guess. Here, there should be at least two arguments: one representing the set of integers for which is the prize door and a second representing the set of integers for which door the contestant guessed in each simulation. 

```{r}
## add your code here

```

#### Problem 4 

Write a function, `switch_guess()`, that represents the strategy of always switching a guess after the goat door is opened. 

```{r}
## add your code here

```

#### Problem 5 

Calculate the percent of correct guesses out of `nsims` using the strategy of switching and the strategy of staying with the first choice made. 

```{r}
## add code here 

```

Most people find this result surprising the first time they hear about the game. Let's explore this a bit more. 

#### Problem 6

Generalize the functions to allow for more than 3 doors. This will help us understand why opening a goat door affects the odds of winning. For example, let's say there are 100 doors in the game now with still only one prize and 99 doors with goats behind them. You pick one door and the host opens 98 other doors after you made your initial selection. Would you want to keep your first pick or switch? 

```{r}
## add code here 

```

What's going on here? 

#### Add your explanation below
